A Method for Regularization of Evolutionary Polynomial Regressions

### 2013-12-20 texts/submission_02-asc/paper_spfga-review.tex
Completed text revision in subsection 2.3.

The polynomial regression \ac{rmse} considered so far accounts for the ability to predict the transformed test-set. A known problem of using a cost function based only in the dataset \ac{rmse} (and of polynomial regressions in general) is the tendency to overfit  training data. This excessive variance can be reduced by regularizing the \ac{rmse} function and one possible method is the inclusion of a penalty factor proportional to the number of monomials. In this line the error from equation \ref{eq:rmse} defines a regularized version
\begin{eqnarray}
J_{\textrm{reg}}\left(\Theta, \lambda;\mathcal{Q},\mathcal{D}\right) &=& \lambda^{k} J_{\textrm{fit}}\left(\Theta;\mathcal{Q},\mathcal{D}\right)\label{eq:rmse-reg}
\end{eqnarray}
%
where $k$ is the number of monomials in the polynomial. When $\lambda > 1$ polynomials with more monomials are penalized. The regularized extension of \ac{EPR}, denoted by \ac{EPRR}, includes the regularized cost function.

@@

\subsection{Genetic Operators}

To perform the genetic algorithm it was used the R package genalg~\citep{Willighagen:2012aa}. The operators were the standard ones: (a)~crossover, \emph{i.e.}, a pair of solutions from the previous generations are combined by splitting and mixing their respective representations, and (b)~mutation, changing the values of single bits; the mutation chance applied in the datasets was 5\%. There was also elitism between generations, \emph{i.e.}, 20\% of the best solutions survive to the next generation.

@@

\begin{figure*}[tb]\begin{center}
\includegraphics[width=0.98\textwidth]{figure_2.pdf}
\note{Plots of ``Regression Trees'' and ``Conditional Inference Trees'' look the same!}
\caption{Results for Artificial dataset. As shown, polynomial regression finds the exact polynomial structure that generates the dataset, reducing the test set prediction error to zero.  The regression methods depicted are: 1. \ac{EPRR}, 2. Linear Regression, 3. SVM, 4. Regression Trees and 5. Conditional Inference Trees}
\label{artificial_dataset1_lambda1.0}
\end{center}\end{figure*}

@@

Comparing \ac{EPR} and \ac{EPRR} -- which is the main article's topic -- the regularized version achieved much better results at Abalone and especially Kinematics. The Housing improved errors when compared with \ac{EPR} in a difference in means, resulted in a 95\% HDI (Highest Density Interval) equal to [0.001, 0.119] which, while borderline, achieves statistical significance. Only in the Auto MOG dataset \ac{EPR} achieved better results, even if not that different from \ac{EPRR}.

>>>>

The polynomial regression \ac{rmse} considered so far accounts for the ability to predict the transformed test-set. A known problem of using a cost function based only in the dataset \ac{rmse} (and of polynomial regressions in general) is the tendency to overfit  training data.

Excessive variance of the estimation method can be reduced by regularizing the \ac{rmse} function with a penalty factor. Thus, to reduce polynomial complexity and variance by regularizing the size of the monomial set the \ac{rmse} function from equation \ref{eq:rmse} is multiplied by a factor $\lambda^{k}$
\begin{eqnarray}
J_{\textrm{reg}}\left(\Theta, \lambda;\mathcal{Q},\mathcal{D}\right) &=& \lambda^{k} J_{\textrm{fit}}\left(\Theta;\mathcal{Q},\mathcal{D}\right)\label{eq:rmse-reg}
\end{eqnarray}
%
where $k$ is the number of monomials in the polynomial. When $\lambda > 1$ polynomials with more monomials are penalized. The regularized extension of \ac{EPR} is denoted by \acf{EPRR}.

@@

\subsection{Genetic Algorithm Parameterization}

In general \acp{GA} offer many possibilities with respect to the choice of genetic operators and respective application rates, population evolution, \emph{etc}. The results found here where obtained using the package \texttt{genalg}~\citep{Willighagen:2012aa} with default parameters, standard operators (crossover and mutation) and population evolution with 20\% elitism between generations.

@@

\begin{figure*}[tb]\begin{center}
\includegraphics[width=0.98\textwidth]{figure_2.pdf}
\note{Plots of ``Regression Trees'' and ``Conditional Inference Trees'' look the same!}
\caption{Results for Artificial dataset. As shown, polynomial regression finds the exact polynomial structure that generates the dataset: in line 1, the error box is centered in $0$ and has width $0$.  The regression methods depicted are: 1. \ac{EPRR}, 2. Linear Regression, 3. SVM, 4. Regression Trees and 5. Conditional Inference Trees}
\label{artificial_dataset1_lambda1.0}
\end{center}\end{figure*}

@@

Comparing \ac{EPR} and \ac{EPRR} -- which is the main article's topic -- the regularized version achieved much better results at Abalone and especially Kinematics. The Housing improved errors when compared with \ac{EPR} in a difference in means, resulted in a 95\% HDI (Highest Density Interval) equal to [0.001, 0.119] which, while borderline, achieves statistical significance. Only in the Auto MPG dataset \ac{EPR} achieved better results, even if not that different from \ac{EPRR}.
